Evaluating a simplified forecast model in comparison to the European forecasting hub ensemble

### 2022-09-27 paper/paper.Rmd
add bias plot for #15

```{r relative-interval-score}
relative_interval_score <- scores |>
  calc_relative_score(
    cols = c("location", "target_end_date", "horizon", "range")
  )

@@

```{r assemble-eval, fig.height = 12, fig.width = 12, out.width = "95%", fig.cap = "Relative weighted interval score by location, horizon, and forecast date for the surrogate forecast model compared to the ensemble forecast model on the log scale. a.) The density of the relative score by horizon. Horizontal black lines give the 5\\%, 35\\%, 65\\%, and 95\\% quantiles. b.) The density of the relative score by month for a given forecast horizon stratified by the one and four-week forecast horizon. c.) The density of the relative score by forecast location stratified by the one and four-week forecast horizon. The dashed line on all plots indicates when the ensemble forecast is equivalent to the surrogate forecast. The vertical black lines on the y-axis give individual relative scores."}
p <- (
  (
    (
      plot_rwis_horizon / plot_rwis_by_month
    )  +
    plot_layout(heights = c(4, 5), guides = "collect")
  ) |
  (
    plot_relative_summary(relative_summary) +
    plot_rwis_location +
    plot_layout(heights = c(1, 7), guides = "collect")
  )
) +
  plot_layout(guides = "collect", widths = c(1, 1)) +
  plot_annotation(tag_levels = "a") &
  theme(
    legend.position = "bottom", legend.margin = margin(),
    legend.justification = "centre"
  )
suppressWarnings(print(p))
```

@@

Stratifying calibration by quantile and forecast horizon the ensemble forecast was overly certain at all horizons for quantiles larger than the median whilst being comparably well calibrated for intervals below the median (Figure \@ref(fig:plot-coverage) c).
This behaviour became more prominant as forecast horizon increased.
In contrast, the surrogat forecast was generally equally well calibrated at across horizons with a tendency to over cover for intervals above the median.
At longer horizons, however, quantiles below the median became liable to have under coverage.

Breaking down the relative weighted interval score by forecast interval we observe that the surrogate modeel produces forecasts that differ most from the ensemble in the outer intervals and in particular the tails of the forecast (Figure \@ref(fig:plot-coverage) b).
This is true across forecast horizons but the magnitude of the difference increases.

```{r plot-coverage, fig.height = 12, fig.width = 18, out.width = "95%", fig.cap = "a.) Empirical coverage of the surrogate and ensemble forecasts at the 90\\%, 60\\%, and 30\\% prediction intervals stratified by forecast horizon. Ideally, a well-calibrated forecast should have empirical coverage for a given prediction interval that equals the range of that interval (i.e 90\\%). b.) Median relative weighted interval score by quantile and forecast horizon for the surrogate forecast compared to the ensemble forecast. c.) Empirical coverage by quantile for both the surrogate and ensemble forecasts. A well-calibrated forecast should have empirical quantiles that match the theoretical ones. The green area of this figure corresponds to conservative forecasts."}
p <- (
  (
    (
      plot_coverage_range(coverage, ranges) /
      plot_rel_score_by_quantile(relative_interval_score)
    )  +
    plot_layout(heights = c(3, 1), guides = "collect")
  ) |
  plot_coverage_quantiles(scores)
) +
  plot_layout(widths = c(1, 2), guides = "collect") +
  plot_annotation(tag_levels = "a") &
  theme(
    legend.position = "bottom", legend.margin = margin(),
    legend.justification = "centre"
  )
suppressWarnings(print(p))
```

>>>>

```{r relative-interval-score}
summary_performance <- scores |>
  summarise_scores(by = c("model", "horizon"))

relative_interval_score <- scores |>
  calc_relative_score(
    cols = c("location", "target_end_date", "horizon", "range")
  )

@@

```{r assemble-eval, fig.height = 12, fig.width = 12, out.width = "95%", fig.cap = "Relative weighted interval score by location, horizon, and forecast date for the surrogate forecast model compared to the ensemble forecast model on the log scale. a.) The density of the relative score by horizon. Horizontal black lines give the 5\\%, 35\\%, 65\\%, and 95\\% quantiles. b.) The density of the relative score by month for a given forecast horizon stratified by the one and four-week forecast horizon. c.) The average relative weighted interval score and absolute error for the surrogate model compared to the ensemble forecast by forecast horizon. d.) The density of the relative score by forecast location stratified by the one and four-week forecast horizon. The dashed line on all plots indicates when the ensemble forecast is equivalent to the surrogate forecast. The vertical black lines on the y-axis give individual relative scores."}
p <- (
  (
    (
      plot_rwis_horizon / plot_rwis_by_month
    )  +
    plot_layout(heights = c(4, 5), guides = "collect")
  ) |
  (
    plot_relative_summary(relative_summary) +
    plot_rwis_location +
    plot_layout(heights = c(1, 7), guides = "collect")
  )
) +
  plot_layout(guides = "collect", widths = c(1, 1)) +
  plot_annotation(tag_levels = "a") &
  theme(
    legend.position = "bottom", legend.margin = margin(),
    legend.justification = "centre"
  )
suppressWarnings(print(p))
```

@@

Stratifying calibration by quantile and forecast horizon the ensemble forecast was overly certain at all horizons for quantiles larger than the median whilst being comparably well calibrated for intervals below the median (Figure \@ref(fig:plot-coverage) b).
This behaviour became more prominant as forecast horizon increased.
In contrast, the surrogat forecast was generally equally well calibrated at across horizons with a tendency to over cover for intervals above the median.
At longer horizons, however, quantiles below the median became liable to have under coverage.

Breaking down the relative weighted interval score by forecast interval we observe that the surrogate modeel produces forecasts that differ most from the ensemble in the outer intervals and in particular the tails of the forecast (Figure \@ref(fig:plot-coverage) c).
This is true across forecast horizons but the magnitude of the difference increases.

```{r plot-coverage, fig.height = 12, fig.width = 18, out.width = "95%", fig.cap = "a.) Empirical coverage of the surrogate and ensemble forecasts at the 90\\%, 60\\%, and 30\\% prediction intervals stratified by forecast horizon. Ideally, a well-calibrated forecast should have empirical coverage for a given prediction interval that equals the range of that interval (i.e 90\\%). b.) Empirical coverage by quantile for both the surrogate and ensemble forecasts. A well-calibrated forecast should have empirical quantiles that match the theoretical ones. The green area of this figure corresponds to conservativ. forecasts. c.) Median relative weighted interval score by quantile and forecast horizon for the surrogate forecast compared to the ensemble forecast. d.) Bias of the ensemble and surrogate forecasts stratified by horizon."}
p <- (
  (
    (
      plot_coverage_range(coverage, ranges)
    )
  ) | (
    plot_coverage_quantiles(scores) + (
      plot_rel_score_by_quantile(relative_interval_score) +
      plot_bias(summary_performance)
    ) +
    plot_layout(heights = c(2, 1), guides = "collect")
  )
) +
  plot_layout(widths = c(1, 2), guides = "collect") +
  plot_annotation(tag_levels = "a") &
  theme(
    legend.position = "bottom", legend.margin = margin(),
    legend.justification = "centre"
  )
suppressWarnings(print(p))
```
